Derive new columns based on given formula

### 2023-04-17 posts/manipulate/formula_derive.qmd
Update formula_derive.qmd

It is the most common in the data manipulation that deriving a column based on a given formula, such as `Toxicity Grade variables`, and `PCSA variables`.

@@

we used the `ifelse` or `case_when` to implemente.In real case, the massive new variables and conditions lead to a not easy life!
here, we can develop functions for functional programmer purpose to handle this kind of task.

>>>>

It is the most common case in the data manipulation that deriving a column based on a given formula, such as `Toxicity Grade variables`, and `PCSA variables`.

@@

we used the `ifelse` or `case_when` to implement the new variables.In real case, the massive new variables and conditions lead to a not easy life!
here, we can develop functions for functional programming purpose to handle this kind of task.
